Appendix

### 2025-04-09 manuscript_rmarkdown/manuscript_appendix.Rmd
Add experimental results for Box-Cox.

>>>>

\begin{table}
\begin{center}
\caption{Residual errors for features from real-world datasets after Box-Cox transformation to normality. 
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling. 
AWT: arterial wall thickness; FE: fuel efficiency; PBM: penguin body mass}
\label{tab:experimental-results-appendix-residuals}
\begin{tabular}{l | r r r r r-bc}

\midrule
none                                  & 16.5 & 110.1 &  54.5 & 328.4 & 48.0 \\
conventional                          & 11.5 &  33.5 &  55.7 & 318.9 & 32.2 \\
conventional (z-score norm.)          & 12.9 &  44.5 &  58.8 & 305.3 & 27.3 \\
conventional (robust scaling)         & 12.9 &  44.7 &  59.0 & 305.3 & 27.3 \\
Raymaekers-Rousseeuw                  & 11.5 & 127.1 &  47.6 & 314.8 & 32.2 \\ 
Raymaekers-Rousseeuw (z-score norm.)  & 13.1 &  54.8 & 127.5 & 510.2 & 23.6 \\
Raymaekers-Rousseeuw (robust scaling) & 18.9 & 100.2 & 113.7 & 510.2 & 23.6 \\
invariant                             & 11.6 &  28.0 &  48.4 & 311.8 & 27.3 \\
robust invariant                      & 12.8 & 150.1 &  60.5 & 646.0 & 27.4 \\

\begin{table}
\begin{center}
\caption{Transformation parameter $\lambda$ for features from real-world datasets after Box-Cox transformation to normality. 
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling. 
AWT: arterial wall thickness; FE: fuel efficiency; PBM: penguin body mass}
\label{tab:experimental-results-appendix-lambda-bc}
\begin{tabular}{l | r r r r r}

conventional                          & 1.9 & -0.5 & -0.1 & 62.1 & -0.5 \\
conventional (z-score norm.)          & 1.2 &  0.1 &  0.2 &  1.2 &  0.5 \\
conventional (robust scaling)         & 1.2 &  0.1 &  0.1 &  1.2 &  0.5 \\
Raymaekers-Rousseeuw                  & 1.9 &  1.1 &  0.8 & 95.9 & -0.5 \\
Raymaekers-Rousseeuw (z-score norm.)  & 1.2 &  0.6 & -0.5 &  0.6 &  0.3 \\
Raymaekers-Rousseeuw (robust scaling) & 0.9 &  1.0 & -0.5 &  0.6 &  0.3 \\
invariant                             & 1.7 & -1.0 & -0.7 &  1.9 &  0.5 \\
robust invariant                      & 1.3 &  1.2 &  1.1 &  0.4 &  0.1 \\

\begin{table}
\begin{center}
\caption{
p-values of empirical central normality tests for features from real-world datasets after Box-Cox transformation to normality.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling. 
AWT: arterial wall thickness; FE: fuel efficiency; PBM: penguin body mass}
\label{tab:experimental-results-appendix-p-value-bc}
\begin{tabular}{l | r r r r r}

none                                  & 0.694 & 0.832 & 0.727     & $< 0.001$ & $< 0.001$ \\
conventional                          & 0.961 & 0.002 & $< 0.001$ & $< 0.001$ & 0.101 \\
conventional (z-score norm.)          & 0.901 & 0.005 & $< 0.001$ & $< 0.001$ & 0.154 \\
conventional (robust scaling)         & 0.901 & 0.005 & $< 0.001$ & $< 0.001$ & 0.154 \\
Raymaekers-Rousseeuw                  & 0.961 & 0.871 & 0.365     & $< 0.001$ & 0.101 \\
Raymaekers-Rousseeuw (z-score norm.)  & 0.891 & 0.268 & $< 0.001$ & $< 0.001$ &	0.495 \\
Raymaekers-Rousseeuw (robust scaling) & 0.562 & 0.789 & $< 0.001$ & $< 0.001$ &	0.492 \\
invariant                             & 0.962 & 0.004 & $< 0.001$ & $< 0.001$ &	0.154 \\
robust invariant                      & 0.899 & 0.890 & 0.866     & $< 0.001$ & 0.622 \\
